ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/evaluation.tex
arrows
Replace ShrinkNet with macro

The \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset contains $581012$
descriptions of geographical area (elevation, inclination, etc...) and the goal
is to predict the type of forest growing in each area. We picked this dataset
for two reasons. First it is simple, such that we can reach good accuracy with
only a few fully-connected layers. This is important because we want to show
that \textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if
we are sampling the entire space of possible network sizes. Second, Scardapane
et al~\cite{Scardapane2017} perform their evaluation on this dataset, which
allows us to compare the results obtained by our method with the method in
~\cite{Scardapane2017}.

@@

\begin{figure*}[t]\centering
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary}
\vspace*{-5mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\end{center}
\vspace*{-4mm}
\end{minipage}
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
}
\end{center}
\vspace*{-4mm}
\end{minipage}
\end{figure*}

>>>>

The \texttt{COVERTYPE} \cite{Blackard:1998:CNN:928509} dataset contains $581012$
descriptions of geographical area (elevation, inclination, etc...) and the goal
is to predict the type of forest growing in each area. We picked this dataset
for two reasons. First it is simple, such that we can reach good accuracy with
only a few fully-connected layers. This is important because we want to show
that \shrink find sizes as good as \textit{Static Networks}, even if
we are sampling the entire space of possible network sizes. Second, Scardapane
et al~\cite{Scardapane2017} perform their evaluation on this dataset, which
allows us to compare the results obtained by our method with the method in
~\cite{Scardapane2017}.

@@

\begin{figure*}[t]\centering
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
\vspace*{-5mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\end{center}
\vspace*{-4mm}
\end{minipage}
\begin{minipage}{2.7in}
\begin{center}
\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
\vspace*{-5mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
\srm{label the x axes on the bottom plots; change ``Desired accuracy`` ``Accuracy''}
}
\end{center}
\vspace*{-4mm}
\end{minipage}
\end{figure*}
